Type Refinements for the Working Class

### 2015-11-13 paper.tex
Add little annotations to make diagrams clearer
Clean up diagram code; use \null
More cleanup; make row/col seps more visible
Fix chktex warnings

For any abt signature $\Match{\Sigma}{\Pair{\Sorts}{\Operators}}$, we can deploy
a generic logical framework. Recall from \cite{sterling-morrison:2015} that
$\SCtx$ is the category of symbol-contexts and their injective, sort-preserving
renamings. Then, fix a small category $\mathcal{W}$ of worlds along with a map
$\Of{\pi}{\mathcal{W}\to\SCtx}$ such that $\pi$ is a Grothendieck
fibration~\cite{jacobs:2001, taylor:1999}:
\[
  \begin{tikzcd}[cramped, ampersand replacement = \&, row sep = large]
    {\IMode{\mathcal{W}}}
      \arrow[dash, d]
    \&
    {\IMode{{w}_{i}}}
      \arrow[drrr]
      \arrow[dotted, dr]
      \arrow[mapsto, dd]
    \&
    {}\&
    {}\&
    {}\\
    {\IMode{{\pi}}}
      \arrow[d]
    \&
    {}\&
    {\OMode{{w}_{j}}}
      \arrow[rr, swap, "\OMode{{\iota}_{\varrho}}"]
      \arrow[mapsto, dd, bend right = 50]
      \arrow[mapsto, d]
    \&
    {}\&
    |[alias = Wk]|{\IMode{{w}_{k}}}
      \arrow[mapsto, d]
    \\
    {\IMode{\SCtx}}\&
    |[alias = Ui]|{\IMode{{\Upsilon}_{i}}}
      \arrow[dr]
    \&
    {\OMode{\scriptstyle{{\pi}({w}_{j})}}}
      \arrow[rr, "\OMode{{\pi}({\iota}_{\varrho})}", ""{name = Msrc, swap}]
      \arrow[equals, d]
    \&
    {}\&
    {\IMode{\scriptstyle{{\pi}({w}_{k})}}}
      \arrow[equals, d]
    \\
    {}\&
    {}\&
    {\IMode{{\Upsilon}_{j}}}
      \arrow[rr, swap, "{\IMode{\varrho}}", ""{name = Mtgt, swap}]
    \&
    {}\&
    |[alias = Uk]|{\IMode{{\Upsilon}_{k}}}
    \arrow[mapsto, from = Wk, to = Uk, bend right = 50, crossing over]
    \arrow[equals, from = Msrc, to = Mtgt]
    \arrow[from = Ui, to = Uk, crossing over]
  \end{tikzcd}
\]
Then, a \emph{judgment} shall be interpreted as an object in the presheaf
category $\Define{\mathbb{J}}{\Sets^{\OpCat{\mathcal{W}}}}$; in other words, a
judgment is identified with the intensional set of its renaming-sensitive
derivations.

@@

   Intuitively, the general judgment $\GenJ{\Omega}{\mathcal{J}}$ is evident
   when the family of judgments $\mathcal{J}$ shall forevermore have a global
   section (i.e. for any substitution $\Member{\vec{E}}{\square\Omega}$,
   $\mathcal{J}(\vec{E})$ shall be evident). Recall that metavariables have
   \emph{valences} rather than sorts; as such, the general judgment allows us
   to quantify over terms of higher type.

>>>>

For any abt signature $\Match{\Sigma}{\Pair{\Sorts}{\Operators}}$, we can deploy
a generic logical framework. Recall from~\cite{sterling-morrison:2015} that
$\SCtx$ is the category of symbol-contexts and their injective, sort-preserving
renamings. Then, fix a small category $\mathcal{W}$ of worlds along with a map
$\Of{\pi}{\mathcal{W}\to\SCtx}$ such that $\pi$ is a Grothendieck
fibration~\cite{jacobs:2001, taylor:1999}:
\[
  \begin{tikzcd}[cramped, ampersand replacement = \&, row sep = large]
    {\IMode{\mathcal{W}}}
      \arrow[dash, d]
\&
    {\IMode{{w}_{i}}}
      \arrow[drrr]
      \arrow[dotted, dr]
      \arrow[mapsto, dd]
\&
    \null
\&
    \null
\&
    \null
\\
    {\IMode{{\pi}}}
      \arrow[d]
\&
    \null
\&
    {\OMode{{w}_{j}}}
      \arrow[rr, swap, "\OMode{{\iota}_{\varrho}}"]
      \arrow[mapsto, dd, bend right = 50]
      \arrow[mapsto, d]
\&
    \null
\&
    |[alias = Wk]|{\IMode{{w}_{k}}}
      \arrow[mapsto, d]
\\
    {\IMode{\SCtx}}
\&
    |[alias = Ui]|{\IMode{{\Upsilon}_{i}}}
      \arrow[dr]
\&
    {\OMode{\scriptstyle{{\pi}({w}_{j})}}}
      \arrow[rr, "\OMode{{\pi}({\iota}_{\varrho})}", ""{name = Msrc, swap}]
      \arrow[equals, d]
\&
    \null
\&
    {\IMode{\scriptstyle{{\pi}({w}_{k})}}}
      \arrow[equals, d]
\\
    \null
\&
    \null
\&
    {\IMode{{\Upsilon}_{j}}}
      \arrow[rr, swap, "{\IMode{\varrho}}", ""{name = Mtgt, swap}]\&
    \null
\&
    |[alias = Uk]|{\IMode{{\Upsilon}_{k}}}
      \arrow[mapsto, from = Wk, to = Uk, bend right = 50, crossing over]
      \arrow[equals, from = Msrc, to = Mtgt]
      \arrow[from = Ui, to = Uk, crossing over]
  \end{tikzcd}
\]
Then, a \emph{judgment} shall be interpreted as an object in the presheaf
category $\Define{\mathbb{J}}{\Sets^{\OpCat{\mathcal{W}}}}$; in other words, a
judgment is identified with the intensional set of its renaming-sensitive
derivations.

@@

   Intuitively, the general judgment $\GenJ{\Omega}{\mathcal{J}}$ is evident
   when the family of judgments $\mathcal{J}$ shall forevermore have a global
   section (i.e.\ for any substitution $\Member{\vec{E}}{\square\Omega}$,
   $\mathcal{J}(\vec{E})$ shall be evident). Recall that metavariables have
   \emph{valences} rather than sorts; as such, the general judgment allows us
   to quantify over terms of higher type.
